Rmarkdown Features

### 2018-03-20 DiagrammeR/rmd_features.rmd
update

## yaml Setup {.tabset}

@@

Include the code in yaml header.
```{yaml}
output:
  html_document:
    df_print: kable
    code_folding: hide
    fig_width: 7
    fig_height: 6
```

@@

### Plotting Expression
```{r fig.height=3}
library(latex2exp)
library(ggplot2)
iris_data2 <- iris[c(1:3, 50:53, 100 :103),] %>% select(Sepal.Length, Sepal.Width, Species)

iris_data2 %>% ggplot() +
    geom_point(mapping = aes(x=Sepal.Length, y=Sepal.Width, color=Species))+
    labs(x=TeX("Length($\\frac{kg}{cm^2}$)"),
         y=TeX("\\frac{a}{b}"))
```

@@

Look at a long footnote[^longnote]
```{markdown}
[^longnote]: Here's one with multiple blocks.

@@

    In this way, multi-paragraph footnotes work like multi-paragraph list items.
```

>>>>

## yaml Setup {.tabset}
Include the code in yaml header.

@@

```{yaml}
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    code_folding: hide
    fig_width: 7
    fig_height: 6
    toc: true
    toc_depth: 4
    toc_float: true
```

@@

### Plotting Expression
```{r fig.height=3}
library(latex2exp)
library(ggplot2)
iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
    select(Sepal.Length, Sepal.Width, Species)

iris_data2 %>% ggplot() +
    geom_point(aes(x = Sepal.Length, 
                   y = Sepal.Width, 
                   color = Species)) +
    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
         y = TeX("\\frac{a}{b}"))
```

@@

```{markdown}
[^longnote]: Here's one with multiple blocks.

@@

    In this way, multi-paragraph footnotes work like multi-paragraph list items.
```
- Output[^longnote].
